Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-11-30 Paper/paper.tex
updated figure 5

\begin{abstract}
Constraining cosmology using Weak Gravitational Lensing consists in comparing measured features with simulated ones. An accurate estimate of the feature covariance matrix is essential to obtain accurate parameter confidence intervals. When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$. We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations. Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent. We also find that, for a range of summary statistics that include shear--shear power spectra measured at different scales and convergence peak counts, parameter constraints degrade faster than the $O(N_b)$ prediction by \citep{DodelsonSchneider13}, where $N_b$ is the length of the feature vector.       
\end{abstract}

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}
\toprule
\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
\midrule
Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
\bottomrule
\end{tabular}
\end{center}
\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{effectivenb}.}
\label{featuretable}
\end{table*}

\begin{figure*}
\includegraphics[scale=0.3]{Figures/effective_nb.eps}
\includegraphics[scale=0.3]{Figures/effective_nb_gaussian.eps}
\caption{Effective dimesionality of the feature space, $D$, as a function of the number of bands $N_b$, for the features outlined in Table \ref{featuretable}. The left panel shows the case in which the feature ensembles are measured from our shear simulations, while in the right panel these ensembles have been replaced by independent draws from a Gaussian multivariate distribution with mean computed from \texttt{NICAEA} and diagonal covariance from equation (\ref{gaussianvar}). The solid black lines show theory predictions.}
\label{effectivenb}
\end{figure*}

@@

@@

Figure \ref{wvar_nr} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}). Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint. Finally Figure \ref{effectivenb} shows how the effective feature dimensionality $D$ depends on the number of bands $N_b$, for a variety of features and binning choices outlined in Table \ref{featuretable}. This behavior is compared with the one that we obtain when the power spectrum ensembles $P_r^{\kappa\kappa}$ are replaced with 1000 independent random samples from a multivariate Gaussian distribution with mean $P^{\kappa\kappa}(l)$ (computed with \texttt{NICAEA}) and diagonal covariance given by equation (\ref{gaussianvar}).

@@

We determine the effective dimensionality of the feature space, $D$, with a linear regression using equation (\ref{ourscaling}), for the set of features outlined in Table \ref{featuretable}. The results shown in Figure \ref{effectivenb}, however, show that the feature dimensionality $D$ grows faster than the linear $O(N_b)$ optimistic prediction by \citep{DodelsonSchneider13}.

>>>>

\begin{abstract}
Constraining cosmology using Weak Gravitational Lensing consists in comparing measured features with simulated ones. An accurate estimate of the feature covariance matrix is essential to obtain accurate parameter confidence intervals. When this covariance matrix $\bb{C}$ is measured from simulations, an important question to ask is how big the simulation set should be for an accurate estimation of $\bb{C}$. We construct different mock ensembles with $N_r$ realizations of the same shear field, based on $N_s<N_r$ independent $N$--body simulations. Using the shear--shear power spectrum as a summary statistic, we find that a single $N$--body simulation can be recycled a large number of times to produce an ensemble of $N_r=10^5$ shear realizations that are mutually independent.       
\end{abstract}

@@

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}
\toprule
\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
\midrule
Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & $\times$ & black  \\
Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\ \hline
Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{OliveGreen}{$+$} & \textcolor{OliveGreen}{green}  \\ 
Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{OliveGreen}{$\bigstar$} & \textcolor{OliveGreen}{green}  \\ 
High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{OliveGreen}{$\diamond$} & \textcolor{OliveGreen}{green}  \\
Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\ \hline
\bottomrule
\end{tabular}
\end{center}
\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{curvingnb}.}
\label{featuretable}
\end{table*}

\begin{figure}
\includegraphics[scale=0.3]{Figures/curving_nb.eps}
\caption{Expectation value of the $w$ variance computed with equation (\ref{estimatorcovariance}) as a function of $1/N_r$, for the features outlined in Table \ref{featuretable}. The line width increases with the number of bands $N_b$ used for each feature.}
\label{curvingnb}
\end{figure}

@@

Figure \ref{wvar_nr} show the scaling of the expectation value of $\h{\sigma}_w^2$ with the number of mocks $N_r$ using the power spectrum and compare it with the known result obtained in \citep{DodelsonSchneider13} and expressed in equation (\ref{ourscaling}). Figure \ref{wvar_ns} shows the effect of varying $N_s$ on the $w$ constraint. Finally Figure \ref{curvingnb} shows....

@@
